Based on the provided structure and documentation, here's an adaptation for a developer audience:

---

### Euronym Developer Documentation

Euronym is a place name labeling solution tailored for multi-scale web mapping applications, majorly focusing on Europe. This documentation aims to provide developers with a comprehensive understanding of Euronym's underlying algorithms, data structures, and methods to ensure effective implementation or modification.

#### Overview:
Euronym employs an advanced [label placement algorithm](https://en.wikipedia.org/wiki/Automatic_label_placement) which dynamically alters the density, selection, and size of place labels based on the user's zoom level and the label's significance.

##### Dynamic Label Adaptation:
View the dynamic change in label density and size with changing zoom levels [here](https://eurostat.github.io/gridviz/examples/labels_.html).

#### API Specifications:

**Base URL**: 
`https://raw.githubusercontent.com/euronym/Nuts2json/master/pub/v2`

Developers can also set up their [own deployment](#own-deployment) and define their own base URL.

**URL Structure**: 
`/<ENCODING>/<RESOLUTION>/<GEO>.csv`

Example:
[`https://raw.githubusercontent.com/eurostat/euronym/main/pub/v2/UTF/100/LU.csv`](https://raw.githubusercontent.com/eurostat/euronym/main/pub/v2/UTF/100/LU.csv)

##### Parameters:

| Parameter | Values | Details |
| ------------- | ------------- |-------------|
| `ENCODING` | `UTF` `ASCII` | Encoding type; default is `UTF`. |
| `RESOLUTION` | `20` `50` `100` `200` | Zoom level for visualization (*m/pixel*). Lower values increase label density and file size. |
| `GEO` | Various GEO codes, like [here](https://github.com/eurostat/euronym/tree/main/pub/v2/UTF/20). `EUR` fetches the entire dataset. | Geographic entity code. |

For deeper API parameter exploration or contributions, please raise an [issue here](https://github.com/eurostat/euronym/issues/new).

#### Data Format:

The data returned is in CSV format with these columns:

| Column | Description |
| ------------- | ------------- |
| `name` | Text of the place name for map rendering. |
| `lon` | Longitude in ETRS89 ([EPSG 4258](https://spatialreference.org/ref/epsg/etrs89/)). |
| `lat` | Latitude in ETRS89. |
| `rs` & `r1` | Resolution thresholds to determine label visibility and exaggeration respectively. |
| `cc` | Country code when `GEO` is `EUR` for filtering. |

#### Dependencies:

Euronym's label generation process is dependent on:

- [EuroRegionalMap](https://eurogeographics.org/maps-for-europe/euroregionalmap/)
- [European commission town names table](https://ec.europa.eu/regional_policy/en/information/maps/urban-centres-towns)

Transformation logic can be found [here](https://github.com/eurostat/euronym/tree/main/src/) which utilizes the [GeoTools library](https://www.geotools.org).

#### Self-hosting:

For a self-contained deployment:

1. Clone the repository: `git clone <repo-url>`
2. Deploy the `pub` folder on your web server.
3. Access the service using your base URL like `https://www.mydomain.eu/path/to/pub/v2`.

#### Additional Information:

- **Main Contributors**: [jgaffuri](https://github.com/jgaffuri)
- **Current Version**: 2
- **License**: [EuroGeographics Open Data Licence](https://www.mapsforeurope.org/licence) for data; [EUPL 1.2](https://github.com/eurostat/Nuts2json/blob/master/LICENSE) for the code.

For contributions, technical queries, or feedback, kindly create an [issue](https://github.com/eurostat/euronym/issues/new).

---

Note: This documentation has been adapted for a developer audience and aims to highlight the technical intricacies and dependencies of the Euronym tool.