**Manager Version**:

---

### Euronym Overview

**What is Euronym?**
Euronym is a solution for effectively displaying place name labels on web-based maps, particularly those focusing on Europe. Through an advanced algorithm, it adjusts the appearance, size, and quantity of these labels depending on how zoomed-in a user is on a map and the importance of the labels.

**Why is it Useful?**
Think of Euronym as an adaptive signpost system for online maps. Just as road signs on a highway change in detail as one approaches a city, Euronym ensures that map users see the right names at the right zoom levels, offering a more efficient and streamlined map-reading experience.

**Key Benefits:**
1. **Adaptability**: It adjusts according to the zoom level, ensuring an optimal amount of information is displayed.
2. **Precision**: The labels point to exact longitude and latitude points for precise location pinpointing.
3. **Flexibility**: Euronym can be utilized across multiple scales and resolutions.
4. **Integration with Gridviz**: A prominent application, Gridviz, utilizes Euronym, showcasing its potential for broad use in various platforms.

**Source Data**: 
The information Euronym uses is derived from established datasets, ensuring accuracy and reliability. This data is sourced from the EuroRegionalMap and the European commission town names table.

**Licensing & Copyright**: 
While the code behind Euronym is licensed under EUPL 1.2, the map data itself is protected by the EuroGeographics Open Data Licence. It's essential to attribute this data to EuroGeographics when used.

**Contribution & Support**: 
For those interested in contributing to or seeking assistance with Euronym, there are avenues available for support, feedback, and collaboration.

**Final Note**: 
The labels and designations used in maps with Euronym are neutral and don't express any political opinions or biases. This ensures a factual and neutral representation of geographic information.

---

Note: This version is tailored to provide a high-level understanding of Euronym to non-technical managers. It focuses on its purpose, benefits, and implications, without delving into the technical details of how it operates.