**Manager Version:**

---

# Euronym Overview

## What is Euronym?

Euronym is a tool that helps in providing name labels for places in web-based maps, especially those focusing on Europe. Simply put, when you zoom in and out on a map, the tool decides which place names to show, how large they should appear, and how dense they should be based on the level of zoom.

## Why is it Beneficial?

- **Adaptability**: Euronym automatically adjusts the labels based on the zoom level. This ensures that your map looks clean and not cluttered with labels, enhancing the user experience.
  
- **Relevance**: With Euronym, you get the most relevant place names displayed at every zoom level. So, users see only what's most important at that specific view.

- **Focus on Europe**: While many mapping tools exist, Euronym specializes in European geographic data, ensuring a more accurate and tailored experience for users interested in European regions.

## How is it Being Used?

An example of Euronym in action is seen in the [Gridviz](https://github.com/eurostat/gridviz/blob/master/docs/reference.md#showing-labels) library. This is a visual example of how the tool ensures optimal label placements on maps.

## Data Sources and Reliability

Euronym is backed by reputable data sources:
- It uses the [EuroRegionalMap](https://eurogeographics.org/maps-for-europe/euroregionalmap/) provided by [EuroGeographics](https://eurogeographics.org/), ensuring accurate and up-to-date geographical information.
- It also utilizes the [European commission town names table](https://ec.europa.eu/regional_policy/en/information/maps/urban-centres-towns), guaranteeing that town names are precise.

## Licensing and Copyright

The tool is licensed under the [EuroGeographics Open Data Licence](https://www.mapsforeurope.org/licence) and [EUPL 1.2](https://github.com/eurostat/Nuts2json/blob/master/LICENSE) for its code. This ensures legal use and provides avenues for further development and adaptation as required.

## In Conclusion

Euronym is an advanced yet user-friendly tool designed to enhance web mapping applications, especially those centered on Europe. It promises a clutter-free, relevant, and enriched user experience, making your maps not just informative but also pleasant to navigate.

---

(Note: The above version is tailored for non-technical managers focusing on the broader picture, benefits, and relevance of Euronym rather than its technical intricacies.)