**Developer Version:**

---

**Graph API Overview for Developers:**
- **Primary Function**: Programmatically manage Facebook data, including querying, posting stories, managing ads, photo uploads, etc.
- **Conceptual Model**: 
  - *Nodes*: Represent individual objects like Users, Pages, Groups, etc. Each node has a unique ID.
  - *Edges*: Connections between nodes. E.g., A User node can be connected to multiple Photo nodes.
  - *Fields*: Properties of nodes. Queries can return default fields or custom ones specified in requests.

- **Technical Specifications**:
  - **HTTP Protocol**: Adheres to HTTP/1.1; all endpoints need HTTPS. Compatible with any HTTP library, making it usable with programming languages like Python, JavaScript, etc.
  - **Host URL**: Primary endpoint - graph.facebook.com. Exception: For video uploads, use graph-video.facebook.com.
  - **Access Tokens**: Critical for accessing most Graph API endpoints. Enables data retrieval without compromising user passwords and identifies the app making the request.

- **Querying Nodes**:
  - Default Request: `curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"`. Returns JSON with name and ID.
  - Get Metadata (field details): Append `metadata=1` to any object ID request.
  
- **Special Endpoint**:
  - `/me`: Translates to ID of the person/Page linked to the current access token.

- **Edges & Field Retrieval**:
  - Edge example: Get user photos using `curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"`.
  - Custom Field Requests: Add the `fields` parameter and list the fields needed. E.g., `fields=id,name,email,picture`.

- **Parameter Types**:
  - Primitives: bool, string, int.
  - Lists: JSON arrays: `["item1", "item2"]`.
  - Objects: JSON objects: `{"key1": "value1", "key2": "value2"}`.

- **Data Operations**:
  - **Create/Update**: Some nodes allow field updates with POST. The API can return fields immediately after write operations.
  - **Delete**: Typically done with a DELETE operation on the object ID. Restrictions apply based on the node.

- **Webhooks**: Subscribe to changes or interactions with nodes. Reference: Webhooks documentation.
  
- **Versioning**:
  - Multiple versions with quarterly releases.
  - Specify version with "vX.Y" before the endpoint, like `graph.facebook.com/v4.0/USER-ID`.
  - Without version number: defaults to oldest version. Always specify the version in requests.
  
- **Error Handling**: If a read fails (invalid field request, etc.), the API returns a standard error. Reference: Handling Errors guide.

- **Further References**:
  - **Webhooks**: For node change notifications.
  - **Versioning guide**: Detailed version handling documentation.
  - **Graph API Changelog**: Full version history and changes.

- **Next Steps for Development**:
  - Explore the Facebook Social Graph using the Graph Explorer tool.
  - Begin implementation by fetching user data and understanding response structures.

---

This adapted version targets developers and emphasizes technical specifications and details that are critical for implementation.