**Developer Version:**

---

**Facebook Graph API: Technical Overview**

---

**HTTP & HTTPS Requirements:**

- The Graph API adheres to HTTP/1.1 specifications.
- Ensure all endpoints are accessed over HTTPS.
- The `includeSubdomains` HSTS directive is active on facebook.com; however, this won't impact your Graph API calls.

---

**Endpoint URL:**

- Primary host URL: `graph.facebook.com`
- For video uploads use: `graph-video.facebook.com`

---

**Access Tokens:**

- Almost every endpoint requires an access token.
- Functions:
  1. Retrieve User data without password.
  2. Identify your app, its User, and granted permissions.

[Detailed Access Token Documentation](#)

---

**Nodes & Their Data:**

- Nodes are unique objects, e.g., User, Page, Photo.
- Sample cURL for User node: 
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"
```
- Response:
```json
{
  "name": "Your Name",
  "id": "YOUR-USER-ID"
}
```
- To fetch metadata for a node:
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID?metadata=1&access_token=ACCESS-TOKEN"
```

---

**Special Endpoint `/me`:**

- Translates to the object ID of the token bearer.
- Sample cURL:
```bash
curl -i -X GET "https://graph.facebook.com/me?access_token=ACCESS-TOKEN"
```

---

**Edges - Connecting Nodes:**

- Represents connections between nodes.
- Fetch a User's photos:
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"
```

---

**Fields - Defining the Data:**

- Specify required fields using the `fields` parameter.
- Example, fetch id, name, email, picture:
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID?fields=id,name,email,picture&access_token=ACCESS-TOKEN"
```

---

**Complex Parameters:**

- Parameters can be primitives, lists, or objects.
- List: `["firstitem", "seconditem", "thirditem"]`
- Object: `{"firstkey": "firstvalue", "secondKey": 123}`

---

**CRUD Operations:**

- Publishing: Check [Facebook Sharing Guide](#)
- Updating (e.g., email update):
```bash
curl -i -X POST "https://graph.facebook.com/USER-ID?email=YOURNEW@EMAILADDRESS.COM&access_token=ACCESS-TOKEN"
```
- Read-after-write support varies per endpoint.

---

**Error Handling:**

- Standard error response for failed reads.
- [Error Handling Guide](#)

---

**Deletion Operations:**

- Typically, delete nodes you created with:
```bash
curl -i -X DELETE "https://graph.facebook.com/PHOTO-ID?access_token=ACCESSS-TOKEN"
```

---

**Webhooks:**

- Subscribe to webhooks to get notifications of node changes.

---

**API Versioning:**

- Specify the version with "vX.Y" (e.g., `v4.0`) before the endpoint in your request.
- If unspecified, the oldest available version is used.
- [Versioning Guide](#) | [Graph API Changelog](#)

---

**Integration Resources:**

- Utilize various APIs, SDKs, and platforms from Facebook for development across platforms.

---

**Getting Started:**

- Dive deeper with the [Graph Explorer tool](#) and experiment with some data-fetching requests.