**Developer Version:**

---

### **Facebook Graph API Technical Overview**

#### **HTTP Protocols**
- Uses HTTP/1.1 standards.
- Requires HTTPS for all endpoints.
- Supports any language with an HTTP library (e.g., cURL, urllib).
- IncludeSubdomains HSTS directive is enabled on facebook.com but won't impact API calls.

#### **Endpoint URLs**
- Standard requests: `graph.facebook.com`
- Video uploads: `graph-video.facebook.com`

#### **Authentication: Access Tokens**
- Essential for most Graph API endpoints.
- Functions:
  1. Retrieve user data without needing their password.
  2. Identify the app, user, and data access permissions.
- Refer to access token documentation for implementation details.

#### **Data Structures**
1. **Nodes**: Individual objects with unique IDs (e.g., Users, Pages, Posts).
   - Example request: 
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"
     ```
   - Use `metadata=1` parameter for field details.
  
2. **Edges**: Connections between nodes (e.g., User's photos).
   - Example request: 
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"
     ```

3. **Fields**: Properties of nodes. Specify desired fields using the `fields` parameter.
   - Example request: 
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID?fields=id,name,email,picture&access_token=ACCESS-TOKEN"
     ```

4. **Parameters**:
   - List type in JSON: `["item1", "item2"]`
   - Object type in JSON: `{"key1": "value1", "key2": 123}`

#### **CRUD Operations**
- Create, Update: Some nodes (e.g., email) allow field updates using POST.
- Read-After-Write: Obtain data immediately after publishing/updating. Use `fields` parameter for specific field details.
- Delete: Typically use DELETE on object ID. Restrictions might apply based on node type.

#### **Error Handling**
- Standard error responses on read failure.
- Refer to Handling Errors guide.

#### **Webhooks**
- Real-time notifications for node changes/interactions.
- Check out the Webhooks documentation.

#### **API Versioning**
- Quarterly version releases. Prefix with 'v' in API call.
- Always specify the version to avoid defaulting to the oldest.

#### **Further Resources**
- Delve into other Facebook platforms: APIs, SDKs.
- **Action Item**: Familiarize yourself with the Graph Explorer tool for hands-on experience with the Facebook Social Graph.

---

Note: This version is adapted with a technical audience in mind, focusing on implementation details and technical specifications.