**Developer Version:**

---

## Facebook Graph API: Technical Overview

---

### **1. Introduction:**

The Graph API is Facebook's core tool for data management. It operates over HTTP, supports HTTP/1.1 and mandates HTTPS for all endpoints.

---

### **2. URL & Endpoints:**

- **Base Host URL**: `https://graph.facebook.com/`
- For video uploads: `https://graph-video.facebook.com/`
  
---

### **3. Access Tokens:**

- **Necessity**: Essential for nearly all API endpoints.
- **Functions**:
  1. Bypass user passwords while accessing specific user data.
  2. Identify the calling app, the user, and the data scope.

[Learn More: Access Token Documentation](#)

---

### **4. Nodes:**

- **Definition**: Unique objects, e.g., Users, Pages, Photos, etc.
- **Example Request**:
  ```bash
  curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"
  ```
- **Response Format**: JSON. E.g.,

```json
{
  "name": "Your Name",
  "id": "YOUR-USER-ID"
}
```

---

### **5. Node Metadata:**

- Fetch fields and their details of a node by appending `metadata=1` parameter.
- **Example Request**:
  ```bash
  curl -i -X GET "https://graph.facebook.com/USER-ID?metadata=1&access_token=ACCESS-TOKEN"
  ```

---

### **6. Special Nodes - /me:**

Represents the object ID of the user/page corresponding to the active access token.

```bash
curl -i -X GET "https://graph.facebook.com/me?access_token=ACCESS-TOKEN"
```

---

### **7. Edges:**

Connections between nodes. A user node might have edges to photos, posts, etc.

```bash
curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"
```

---

### **8. Fields:**

Node properties. Define using the `fields` parameter to customize the returned data.

```bash
curl -i -X GET "https://graph.facebook.com/USER-ID?fields=id,name,email,picture&access_token=ACCESS-TOKEN"
```

---

### **9. Complex Parameters:**

- **List**: JSON format. E.g., `["firstitem", "seconditem", "thirditem"]`
- **Object**: JSON format. E.g., `{"firstkey": "firstvalue", "secondKey": 123}`

---

### **10. CRUD Operations:**

- **Create & Update**: Possible with POST operations. Return fields using `fields` parameter.
- **Delete**: Use DELETE operation on the object ID. Restrictions may apply based on the node type.

---

### **11. Webhooks:**

Register to receive real-time notifications on node changes. [Webhooks Documentation](#)

---

### **12. API Versioning:**

- Quarterly version releases.
- Specify version with "v" prefix, e.g., `/v4.0/USER-ID/photos`.

[Versioning Guide](#) & [Graph API Changelog](#)

---

### **13. Facebook SDKs & Platforms:**

Leverage Facebook's SDKs and platforms for cross-platform integrations.

---

### **Next Steps**:

Dive deeper with the Graph Explorer tool to explore more advanced API calls and data fetching techniques.

---