**Developer Version:**

---

**Graph API for Facebook - Technical Documentation**

**Overview:**
The Graph API lets developers interface with the Facebook platform. It's constructed on the foundation of a "social graph" concept and uses an HTTP-based approach. With it, developers can carry out various tasks, including querying, posting, and managing ads. Nodes, edges, and fields are core components of the Graph API.

**HTTP Specifications:**
- **Protocol:** Conforms to HTTP/1.1
- **Security:** Endpoints are HTTPS-only. 
- **HSTS directive:** 'includeSubdomains' has been enabled on facebook.com but shouldn’t interfere with your Graph API operations.

**Endpoints:**
- Primary: `graph.facebook.com`
- Exception: Video uploads use `graph-video.facebook.com`.

**Authentication via Access Tokens:**
- Almost every endpoint necessitates an access token.
- Functions:
  1. Eliminates the need for user passwords when accessing specific user info.
  2. Identification mechanism for apps, user identity, and data permissions.

**Nodes:**
- Represents unique objects with IDs. e.g., Users, Pages, Posts, etc.
- Retrieve a User node with the following cURL:
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"
```
- Metadata for nodes can be fetched by appending `metadata=1` parameter.

**Special Node: /me**
- Represents the object ID of the authenticated person or Page making the API calls.
  
**Edges:**
- Represents connections between nodes.
- Fetch photos linked to a User:
```bash
curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"
```

**Fields:**
- Specific properties of nodes.
- Fields can be customized in requests using the `fields` parameter. By default, object IDs are always returned.
  
**Complex Parameters:**
- Support for `list` and `object` types using JSON syntax.

**CRUD Operations:**
- Use POST operations to publish or update node fields.
- Read-After-Write: Immediately read data after publishing/updating using the `fields` parameter.
- Delete nodes with DELETE operations:
```bash
curl -i -X DELETE "https://graph.facebook.com/PHOTO-ID?access_token=ACCESS-TOKEN"
```

**Webhooks:**
- Subscribe to webhooks to get updates on nodes or interactions.

**API Versions:**
- Released quarterly. Specify versions in calls with `v` followed by the version number.
- Always include a version to avoid defaults to the oldest version.

**Errors:**
- Standardized error responses provided. For a comprehensive guide, refer to Handling Errors.

**SDKs & Platforms:**
Facebook provides multiple APIs, SDKs, and platforms for various development needs.

**Recommendation for First-time Developers:**
For hands-on practice, use the Graph Explorer tool to interact with the Facebook Social Graph.

---

This version focuses on a more technical perspective, shedding light on the nitty-gritty details that would be essential for developers wanting to integrate or modify the Graph API in their applications.