**Developer Version:**

---

### Facebook Graph API Developer Guide

#### Introduction:
The Graph API is Facebook's core API, facilitating data transfer into and out of the platform. It leverages HTTP/1.1 and strictly requires HTTPS for communication.

#### Endpoints:
- Main Host: `graph.facebook.com`
- Video Uploads: `graph-video.facebook.com`

#### Key Concepts:

1. **Access Tokens**: 
   - A must for almost all Graph API calls.
   - Performs user authentication and app authorization.
   - Further info: [Access Token Documentation](#)

2. **Nodes**: 
   - Represents objects with unique IDs. Examples: Users, Pages, Photos.
   - Example call: 
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID?access_token=ACCESS-TOKEN"
     ```
   - Metadata Retrieval: Add `metadata=1` parameter.
   
3. **/me Node**: 
   - Refers to authenticated user or Page's ID.
   
4. **Edges**: 
   - Connections between two nodes, like User-Photo.
   - Example call: 
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID/photos?access_token=ACCESS-TOKEN"
     ```

5. **Fields**: 
   - Node properties.
   - Custom selection using `fields` parameter. Example:
     ```bash
     curl -i -X GET "https://graph.facebook.com/USER-ID?fields=id,name,email,picture&access_token=ACCESS-TOKEN"
     ```

6. **Parameters**:
   - Primitives: bool, string, int.
   - List Type: `["first", "second"]`
   - Object Type: `{"key": "value"}`

7. **CRUD Operations**:
   - Create: Use POST to add data.
   - Read: Send GET with specific fields.
   - Update: Use POST with new data values.
   - Delete: DELETE operation on specific node's ID.
   
8. **Read-After-Write**: 
   - Instantly read data after publishing or updating.
   - Default return is object ID unless fields specified.
   - Example call: 
     ```bash
     curl -i - X POST "https://graph.facebook.com/PAGE-ID/feed?message=Hello&fields=created_time,from,id,message&access_token=ACCESS-TOKEN"
     ```

9. **Errors**: 
   - Handled with standard responses.
   - See: [Handling Errors Guide](#)

10. **Webhooks**:
   - Subscription-based node change notifications.
   
11. **API Versions**: 
   - Quarterly releases.
   - Specify using "v" + version number. E.g., `v4.0`.
   - Default: Oldest version. Recommendation: Always specify.
   - Details: [Versioning Guide](#) & [Graph API Changelog](#)

#### Tools and SDKs:
Harness the power of the Graph API across platforms and interfaces using Facebook's suite of SDKs, APIs, and tools.

#### Dive Deeper:
Start experimenting with the Graph API using the Graph Explorer tool for practical understanding. Explore real-time requests and fetch data from the Facebook Social Graph. 

---

*Note: The above content is tailored for developers, emphasizing technical aspects and actionable code examples.